Sparse Function-space Representation \\ of Neural Networks

### 2023-05-15 paper/main.tex
rewrite intro

%Current state of affairs 
Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) for converting trained neural networks from weight-space to function-space allow a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{add}. These methods rely on the linearization of neural networks\cite{jacot2018neural} the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}). GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they serve as a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}. 
%Yet many problems lie in high dimensional input space; for example, images are where GPs cannot learn representations. In such scenarios such as in many reinforcement learning environments neural networks are used as the surrogate model. However, uncertainty is still essential to ensure effective exploration for sequential algorithms. Successful approaches have attempted to blend neural networks with uncertainty estimates around predictions, allowing for sophisticated exploration strategies. However, there has been limited use of hybrid models that possess the feature representation ability of neural networks but also attractive the properties of GPs, such a hybrid method we propose in this paper.

%Need for adaptive learning methods + failures with current methods
In this paper, we demonstrate that any neural network can be represented in terms of the so-called `dual' parameters of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast}. Contrasting to previous work that use subsets \cite{immer2021scalable}, this parameterization allows squashing the contributions of {\em all} training data into a sparse representation. Crucially, the resulting GP now predicts in the same space as the originally trained neural network, a feature not present in previous approaches, while still avoiding the notorious cubic complexity of vanilla GPs. Given the dual parameter formulation, we establish a link between the neural network, the resulting full GP, and a sparse approximation of it akin to variational sparse GPs~\cite{titsias2009variational}. Using the sparse GP we can then take advantage of the property of dual parameters that allows for fast conditioning recently shown in \cite{chang2022fantasizing}. Thus we are able to avoid retraining and condition new data in to our model. The resultant \our method can be used in any sequential decision-making scenario where retraining is not available.
%\todo{a pragraph on how this can be used for improving CL and RL}

>>>>

%Current state of affairs 
Recent techniques (\eg, \cite{ritter2018kfac,khan2019approximate,daxberger2021laplace,fortuin2021bayesian,immer2021scalable}) for converting trained neural networks from weight-space to function-space allow a principled mathematical approach for analyzing the behaviour \cite{cho2009kernel,meronen2020stationary}, performing probabilistic inference \cite{khan2019approximate}, and quantifying uncertainty in neural networks \cite{foong2019between}. These methods rely on the linearization of neural networks\cite{jacot2018neural} the neural network and capturing the first two moments in function space in terms of a mean function and covariance function (or kernel)---defining a Gaussian process (GP, \cite{rasmussen2006gaussian}). GPs provide a widely-used probabilistic toolkit with principled uncertainty estimates, and they serve as a standard surrogate model for Bayesian optimization \citep{garnett_bayesoptbook_2022} and are effective in model-based reinforcement learning \citep{deisenroth2011pilco} with theoretical guarantees on regret bounds \citep{srinivas2009gaussian}. 
%Yet many problems lie in high dimensional input space; for example, images are where GPs cannot learn representations. In such scenarios such as in many reinforcement learning environments neural networks are used as the surrogate model. However, uncertainty is still essential to ensure effective exploration for sequential algorithms. Successful approaches have attempted to blend neural networks with uncertainty estimates around predictions, allowing for sophisticated exploration strategies. However, there has been limited use of hybrid models that possess the feature representation ability of neural networks but also attractive the properties of GPs, such a hybrid method we propose in this paper.

%Need for adaptive learning methods + failures with current methods
In this paper, we demonstrate that any neural network can be represented in terms of the so-called `dual' parameters of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast}. Contrasting to previous work that use subsets \cite{immer2021scalable}, this parameterization allows squashing the contributions of {\em all} training data into a sparse representation. Crucially, the resulting GP now predicts in the same space as the originally trained neural network, a feature not present in previous approaches, while still avoiding the notorious cubic complexity of vanilla GPs. Given the dual parameter formulation, we establish a link between the neural network, the resulting full GP, and a sparse approximation of it akin to sparse GPs~\cite{titsias2009variational}. Using the sparse GP we can then take advantage of the property of dual parameters that allows for fast conditioning recently shown in \cite{chang2022fantasizing}. Thus we are able to avoid retraining and condition new data in to our model. The resultant \our method can be used in any sequential decision-making scenario where retraining is not available.
%\todo{a pragraph on how this can be used for improving CL and RL}
